Methods for Large Scale Learning to Rank

### 2014-09-29 report/Chapters/Future.tex
naar refactoring werk
future work puntje

\subsection{Computing models}
We explored the possibilities of Hadoop MapReduce for computation

\subsection{Learning to Rank algorithms}

>>>>

\section{Computing models}
We explored the possibilities of Hadoop MapReduce for distributed computation of Learning to Rank training algorithms. Hadoop, since the introduction of Hadoop YARN in Hadoop 2.0, offers integration with other distributed computing models, including Spark \cite{}, Storm \cite{} and MPI \cite{}. Of these distributed programming models, Spark is particularly promising, since Shukla et al. \cite{Shukla2012} already showed that it is able to speed-up the ListNet training procedure with much lower job scheduling overhead than that we found for MapReduce.

\section{Learning to Rank algorithms}
